%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{xcolor}
\definecolor{cBlue}{HTML}{455d7a}
\definecolor{cRed}{HTML}{e23e57}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{%
    colorlinks=true,
    urlcolor = cBlue
}
% \usepackage{fancyhdr}
\usepackage{microtype}

\usepackage[adobe-utopia]{mathdesign}
% \usepackage[T1]{fontenc}
\usepackage{fontawesome}

% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}
\usepackage[margin=0.75in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\color{cRed}
}{}{0em}{}[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Huge{Caleb Geiger}}\\
    \faEnvelope: \url{caleblgeiger@gmail.com}

    & \faGithub: \url{https://github.com/ElodinLaarz}\\
     \faGlobe: \url{https://calebgeiger.org/}
    &
    \faLinkedin: \url{https://www.linkedin.com/in/caleb-geiger/}
    \\
    \faMapO: Hinesville, GA (Open to relocation)
    & Citizenship: USA \\
\end{tabular*}


% --------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
            \textbf{Fluent in: }{Python, Git}
    }
\item{\vspace{-0.15cm}
            \textbf{Prior projects using: }{C++, Javascript, HTML, CSS, C\#, Sage}
    }
  % \item{Python, Git, SQL, Bash, C++, MATLAB, Cython}
  \resumeSubHeadingListEnd
  \vspace{-0.5cm}

%-----------PROJECTS-----------------
\section{Select Personal Projects}
\resumeSubHeadingListStart
\resumeSubItem{WordlBattl}{Inspired by the popularity of the Wordle game, I created a version where you can play against an AI opponent. I also created an accompanying {\it WordlHelpr} that you can use to get ideas for words to try out if you are stuck in your Wordle game. See \url{https://elodinlaarz.github.io/wordlBattl.html}, and play for yourself!
}
\resumeSubItem{HanabiAI}{A project that used genetic learning algorithms to teach an AI to play the card game Hanabi. As a consequence, it also included a text-based implementation of the game of Hanabi to play with the AI. See \url{https://github.com/ElodinLaarz/HanabiAI}.
}
\resumeSubItem{Crypto}{A simple project where I implement Diffie-Hellman Key Exchange in the case of elliptic curves and then attempt to break the encryption using Pollard's Rho algorithm. See \url{https://github.com/ElodinLaarz/CryptoPractice}.
}
\resumeSubItem{APLUnity}{A simple, single, two-dimensional level coded in C\# using Unity. See \url{https://github.com/ElodinLaarz/APLUnity/}}
% \resumeSubItem{Sagemath -- isomorphism testing}{Implemented isomorphism testing of
% modular abelian varieties into the Sagemath Python library. Currently in the
% process of being merged. See \url{https://trac.sagemath.org/ticket/28275}}
% \resumeSubItem{zlong\_alert.zsh}{Zsh plugin for alerting you upon the
% completion of a long-running command. See
% \url{https://github.com/kevinywlui/zlong_alert.zsh}}

\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{University of Washington}{Seattle, WA}
{Researcher in Computational Number Theory}{Sep. 2015 --- Jun. 2020}
\resumeItemListStart
\resumeItem{Overview}
{
    % Thesis research centered around creating and implementing algorithms for
    % computing invariants of modular abelian varieties. I was able to create
    % algorithms for computing certain invariants where existing methods where
    % computationally infeasible or non-existent.
    Thesis research centered around the ideal class group of imaginary quadratic orders by counting the number of ideals of prime powered norm in the case of non-maximal orders. 
}
\resumeItem{Technical skills used}{
    % Code was written using the Sagemath Python library. Experiments were done
    % using Jupyter notebooks. Tables of related invariants were computed and
    % stored in PostgreSQL databases.
    Heavily used Sage and Python when working with these non-maximal orders.
}
\resumeItem{Link to thesis}{\url{https://digital.lib.washington.edu/researchworks/bitstream/handle/1773/45518/Geiger_washington_0250O_21118.pdf}}
\resumeItemListEnd

\resumeSubheading
{Coding Enthusiast}{Online}
{Participant}{2019-Present}
\resumeItemListStart
\resumeItem{Overview}
{
	Google Code Jam (2019 - 2021), qualifying in 2020 and 2021; Google Hash Code (2020 and 2021), placing 1,908th out of 10,724 participants and  2,615th out of 9004 participants, respectively, and I have already signed up for Google Hash code 2022, as well; and finally, foobar.withgoogle (Level 5).
}
\resumeItemListEnd
\resumeSubheading
{Mathematics Instructor}
{Savannah Technical College}{Instructor}{August 2021-Present}
\resumeItemListStart
\resumeItem{Overview}{Instruct and facilitate technical outcomes in the curriculum and proactively support all facets of the learning environment.}
\resumeItemListEnd

\resumeSubheading
{Graduate Student Instructor}
{University of Washington}{Mathematics Instructor}{2015-2020}
\resumeItemListStart
\resumeItem{Overview}{Taught mathematics courses from Precalculus to Differential Equations and Linear Algebra. Awarded {\it Distinguished Teaching Award} from the mathematics department.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Washington, Seattle}{Seattle, WA}
{M.S. in Mathematics, specializing in Algebraic Number Theory}{Sep. 2015
--- Jun. 2020}
% \resumeSubheading
% {University of Washington, Seattle}{Seattle, WA}
% {Masters in Mathematics}{June 2018}
\resumeSubheading
{University of California, Irvine}{Irvine, CA}
{B.S. in Mathematics}{Sep. 2013 --- Jun. 2015}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}